Supplement to ``Local clustering of density upper level sets''

### 2019-01-11 icml/icml_local_density_clustering_supplement.tex
related work complete; theorem 2 added

	Let $t_{i} = i/k$ for $i = 0, \ldots, k$. Taking the limit as $k \to \infty$, we have
	\begin{align*}
	& \lim_{k \to \infty} \sum_{i = 0}^{k-1} \biggl\{ \left(1 + \frac{r (i+1)}{k\sigma}\right)^d - \left(1 + \frac{r i}{k\sigma}\right)^d \biggr\} \left(\tau_{\sigma} - \left(\frac{ri}{k}\right)^{\gamma}\right)  \\
	 & = \int_{0}^{1} \frac{rd}{\sigma} (1 + \frac{r t}{\sigma})^{d-1} (\tau_{\sigma} - (rt)^{\gamma}) dt \\
	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
	\end{align*}
	where the inequality comes from $t \leq 1$ and $r < \sigma$.

@@

\begin{lemma}
	\label{lem: expected_density_cut}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
	\begin{equation*}
	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right)
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write $\widetilde{\mathcal{E}}$ as the sum of indicator functions,
	\begin{equation}
	\label{eqn: density_cut_expansion}
	\widetilde{\mathcal{E}} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig)
	\end{equation}
	Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
	\begin{align*}
	\frac{\widetilde{\mu}}{{n \choose 2}} & = 2 \int_{\Asigr} f(x) \left\{ \int_{B(x,r) \cap \Asig} f(x') dx'\right\} dx \\
	& \overset{(i)}{\leq} 2 \int_{\Asigr} f(x) \nu_d r^d \tau dx \\
	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma + 1}}{\gamma + 1}\right) 
	\end{align*}
	where $(i)$ follows from Assumption \ref{asmp: cluster_separation}, which implies $f(x') \leq \tau$ for all $x' \in \Asig \setminus A$, and $(ii)$ follows from Lemma \ref{lem: expected_number_boundary_points}.
\end{proof}

>>>>

	Let $t_{i} = i/k$ for $i = 0, \ldots, k$. Taking the limit as $k \to \infty$, we have
	\begin{align*}
	& \lim_{k \to \infty} \sum_{i = 0}^{k-1} \biggl\{ \left(1 + \frac{r (i+1)}{k\sigma}\right)^d - \left(1 + \frac{r i}{k\sigma}\right)^d \biggr\} \left(\tau_{\sigma} - \left(\frac{ri}{k}\right)^{\gamma}\right)  \\
	 & = \int_{0}^{1} \frac{rd}{\sigma} (1 + \frac{r t}{\sigma})^{d-1} (\tau_{\sigma} - (rt)^{\gamma}) dt \\
	& \leq 2^{d-1} \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma }}{\gamma + 1}\right)
	\end{align*}
	where the inequality comes from $t \leq 1$ and $r < \sigma$.

@@

\begin{lemma}
	\label{lem: expected_density_cut}
	Under the setup and conditions of Theorem \ref{thm: conductance_upper_bound}, and for any $r < \sigma$,
	\begin{equation*}
	\widetilde{p} \leq \frac{2^d d}{\sigma} \nu(\Asig) \nu_d r^{d+1} \tau \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right)
	\end{equation*}
\end{lemma}
\begin{proof}
	We can write $\widetilde{\mathcal{E}}$ as the sum of indicator functions,
	\begin{equation}
	\label{eqn: density_cut_expansion}
	\widetilde{\mathcal{E}} = \sum_{i = 1}^{n} \sum_{j = 1}^{n} \1(x_i \in \Asigr) \1(x_j \in B(x_i,r) \cap \Asig)
	\end{equation}
	Ignoring the cross terms (which are zero), normalizing by $1/{n \choose 2}$, and taking expectation, we have
	\begin{align*}
	\frac{\widetilde{\mu}}{{n \choose 2}} & = 2 \int_{\Asigr} f(x) \left\{ \int_{B(x,r) \cap \Asig} f(x') dx'\right\} dx \\
	& \overset{(i)}{\leq} 2 \int_{\Asigr} f(x) \nu_d r^d \tau dx \\
	& \overset{(ii)}{\leq} 2^d \nu_d r^d \tau \nu(A_\sigma) \frac{rd}{\sigma} \left(\tau_{\sigma} - \frac{r^{\gamma}}{\gamma + 1}\right) 
	\end{align*}
	where $(i)$ follows from Assumption \ref{asmp: cluster_separation}, which implies $f(x') \leq \tau$ for all $x' \in \Asig \setminus A$, and $(ii)$ follows from Lemma \ref{lem: expected_number_boundary_points}.
\end{proof}
